\section{Results}

\subsection{Distance-Dependent Decoding}
If numerosity is represented as a continuous magnitude, conditions that
are numerically farther apart should produce more distinct neural
patterns and thus higher decoding accuracy. We tested this by grouping
condition-pair decoding accuracies by the absolute difference between
the two conditions' target numerosities and computing the group mean at
each time window.
Figure~\ref{fig:temporal-distance}a shows that pairs separated by
greater numerical distance tend to be decoded more accurately, with
the clearest graded ordering by distance in early (80-200 ms) and mid-latency
(340-500 ms) windows. Across all six numerosities, this graded pattern is consistent with a
distance-dependent neural code.

\paragraph{The ``No-1'' control.}
To assess whether the distance gradient is driven by the inclusion of
numerosity~1, we repeated the analysis excluding all pairs
containing ``1'' (Figure~\ref{fig:temporal-distance}b). Sustained
separation by numerical distance largely disappears, with the clearest
residual distance-related gradient limited to approximately 80-120 ms. This suggests that
numerosity~1 disproportionately drives discriminability.

\input{figures/temporal_distance}

\subsection{Whole-Epoch Analysis}
To compare candidate representational structures, we computed
whole-epoch target RDMs and compared them to theoretical models
(Table~\ref{tab:static-model-comparison},
Figure~\ref{fig:static-model-rdms}).

\input{figures/table_static_model_comparison}

When all six target numerosities (1-6) were included, ANS, Target
PI(1-4), and Target PI(1-3) were all significant
(Table~\ref{tab:static-model-comparison}),
with ANS showing the highest correlation. Target PI(1-4) outperformed
Target PI(1-3) ($d = 0.53$, $p = 0.017$). The Pixel control did not
reach significance, suggesting that low-level image similarity does not
account for the observed neural dissimilarity structure. RT was significant ($r = 0.162$, $p = 0.005$),
indicating that neural dissimilarity structure covaries with RT
differences.

After excluding numerosity~1, Target PI(2-4) remained significant ($r = 0.269$,
$p_{\text{Holm}} = 0.003$), while Target PI(2-3) ($r = 0.076$) and ANS
($r = 0.074$) did not reach significance. The boundary contrast strengthened to $d = 0.79$ ($p < 0.001$).
The Pixel control remained non-significant, whereas RT remained
significant ($r = 0.268$, $p_{\text{Holm}} = 0.007$).
Among the numerosity models, only Target PI(2-4) remained significant
when numerosity~1 was removed.

\paragraph{Multidimensional scaling.} MDS of the whole-epoch brain RDM
(Figure~\ref{fig:static-change6-mds}) visualizes this structure.
Numerosity~1 is isolated, PI-range
numerosities (2-4) group together, and ANS-range numerosities (5-6)
occupy a separate region, consistent with a categorical boundary at 4-5
and with numerosity~1 as a distinct representational case.

\input{figures/static_change6_mds}

\subsection{Time-Resolved Analysis}
%% Queue full-width figures early so LaTeX places them efficiently.
\input{figures/temporal_change24_rdm_snapshots}
\input{figures/temporal_rdm_evolution}
\input{figures/temporal_change24_model_rdms_compact}
To compare candidate representational structures over time, we
computed time-resolved neural RDMs and compared them to theoretical
models (Figures~\ref{fig:temporal-change24-model-fits}-\ref{fig:temporal-change24-model-rdms};
Appendix Table~\ref{tab:appendix-temporal-model-fit-clusters}).
Figure~\ref{fig:temporal-change24-rdm-snapshots} depicts the evolving
representational structure across all 24 prime-target conditions, with
each panel showing the mean neural RDM in a 100 ms bin.
Figure~\ref{fig:temporal-change24-model-fits} plots the corresponding
time-resolved model-fit trajectories, with bottom bars marking
significant clusters, and
Figure~\ref{fig:temporal-change24-model-rdms} presents the mean brain RDM
(0-700 ms average) alongside the theoretical model RDMs.

When all 24 prime-target conditions were included (with numerosity~1;
Figure~\ref{fig:temporal-change24-model-fits}a), Target PI(1-4) showed
two significant clusters (50-250 ms and 270-550 ms, both $p < 0.001$),
and ANS also showed two significant clusters (30-230 ms and 290-530 ms,
both $p < 0.001$). ANS reached the highest single-window model-brain
correlation in the with-1 condition. Full model-fit cluster windows are
reported in Appendix Table~\ref{tab:appendix-temporal-model-fit-clusters}.

When pairs containing ``1'' were excluded
(Figure~\ref{fig:temporal-change24-model-fits}b), Target PI(2-4)
remained significant in two clusters (50-230 ms and 250-510 ms, both
$p < 0.001$), whereas ANS remained significant in narrower clusters
(50-190 ms, $p < 0.001$, and 410-510 ms, $p = 0.003$). This pattern
indicates that removing numerosity~1 attenuates ANS breadth while
preserving 4-5 boundary structure.

\paragraph{Model-difference tests.}
Table~\ref{tab:model-differences}
shows that the 4-5 boundary captures neural structure better than the
3-4 alternative. Target PI(1-4) significantly outperforms Target PI(1-3)
at 230-330 ms ($p < 0.001$), 490-550 ms ($p = 0.039$), and 570-650 ms
($p = 0.014$). A two-sided Target PI(1-4) vs.\ ANS comparison yields one cluster
at 90-150 ms ($p = 0.050$) in which ANS fits the brain data better
than Target PI (negative $\Delta z$). In the no-1 variant, Target PI(2-4)
exceeds ANS at 170-310 ms ($p < 0.001$) and exceeds Target PI(2-3) at
130-350 ms ($p < 0.001$) and 390-550 ms ($p < 0.001$). Together,
these temporal comparisons converge with the whole-epoch results and
show stronger support for the 4-5 boundary when numerosity~1 is
excluded.

\input{figures/table_model_differences}

\paragraph{Multidimensional scaling.} MDS of the 24-condition neural
RDM (Figure~\ref{fig:temporal-change24-mds}) provides visual
confirmation. Conditions separate by target system membership, with target-1
pairs forming an isolated cluster, PI-range targets (2-4) grouping
centrally, and ANS-range targets (5-6) occupying a distinct region.

\input{figures/temporal_change24_mds}
